\documentclass[12pt, a4paper]{article}
\setlength{\parindent}{0pt}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage[a4paper, portrait, margin=1in]{geometry}

% i like the black square better.
\renewcommand{\qedsymbol}{$\blacksquare$}
%\renewcommand{\implies}{\Rightarrow}

\newcommand{\N}{\mathbb{N}}
\newcommand{\ddx}{\frac{d}{dx}}

\newtheorem{theorem}{Theorem}

% let's begin
\begin{document}

\textbf{(Q1)}
The formula is:

\[
    \displaystyle f^{(n)}(x) = \frac{3^n \cdot n!}{(5 - 3x)^{n + 1}}
\]

\begin{proof}
    Since we are only considering $n \in \N$, we prove this through induction. To make
    operations easier to see, we write $f(x)$ as $(5 - 3x)^{-1}$.

    \textit{Base Case.}

    Let $n = 1$. By application of the chain rule:

    \begin{align*}
        f^{(1)}(x) & = -1 \cdot (5 - 3x)^{-2} \cdot \ddx(5 - 3x)\\
        & = -1 \cdot (5 - 3x)^{-2} \cdot -3\\
        & = 3(5 - 3x)^{-2}\\
        & = \frac{3}{(5 - 3x)^2} = \frac{3^1 \cdot 1!}{(5 - 3x)^{1 + 1}}
    \end{align*}

    Thus, the base case holds.

    \textit{Induction Step.}

    In this step, we aim to prove the following induction hypothesis:
    \[
        f^{(n)}(x) = \frac{3^n(n!)}{(5 - 3x)^{n + 1}}
        \implies f^{(n + 1)}(x) = \frac{3^{n + 1} \cdot (n + 1)!}{(5 - 3x)^{(n + 1) + 1}}
    \]

    We begin by simplifying the right hand side of the implication and rewriting it:
    \begin{align*}
        f^{(n + 1)}(x) & = \frac{3^{n + 1} \cdot (n + 1)!}{(5 - 3x)^{(n + 1) + 1}}\\
        & = \frac{3^n \cdot 3 \cdot n! \cdot (n + 1)}{(5 - 3x)^{n + 1} \cdot (5 - 3x)}\\
        & = \frac{3^n(n!)}{(5 - 3x)^{n + 1}} \cdot 3 \cdot (n + 1) \cdot (5 - 3x)^{-1}
    \end{align*}

    We observe that $f^{(n + 1)}(x)$ is simply $f^{(n)}(x)$ multiplied by
    $\left[3 \cdot (n + 1) \cdot (5 - 3x)^{-1}\right]$. Therefore, if the derivative
    of $f^{(n)}(x)$ has the same result, the induction hypothesis is proved.

    Differentiating $f^{(n)}(x)$ via chain rule ($n$ is a constant and is not affected):
    \begin{align*}
        \ddx 3^n(n!)(5 - 3x)^{-(n + 1)} & = 
        3^n(n!)(5 - 3x)^{-(n + 1) - 1} \cdot -(n + 1) \cdot -3\\
        & = 3^n(n!)(5 - 3x)^{-(n + 1) - 1} \cdot (n + 1) \cdot 3 
        \text{ (minus signs cancel)}\\
        & = 3^n(n!)(5 - 3x)^{-(n + 1) } \cdot 
        \left[(5 - 3x)^{-1} \cdot (n + 1) \cdot 3\right]
    \end{align*}

    We observe that these additional terms are the exact same ones we multiplied to $f^{(n)}(x)$ 
    to obtain $f^{(n + 1)}(x)$, thereby proving the induction hypothesis.

    Since both the base case and induction hypothesis hold, we have proven the theorem, as required.
\end{proof}

\end{document}